%-------------------------
% Resume in Latex
% Author : Chun Chet Ng
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{lastpage}
\usepackage{csquotes}
\usepackage{datetime}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\cfoot{\makebox[\textwidth][c]{Page \thepage \hspace{1pt} of \pageref{LastPage}}}

\newdateformat{monthyear}{\shortmonthname[\THEMONTH]. \THEYEAR}
\lfoot{\makebox[\textwidth][l]{\emph{Last updated \monthyear\today}}}
\setlength{\footskip}{14pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeListEnd}{\end{itemize}}

\newcommand{\resumeListStartNum}{\begin{enumerate}[leftmargin=0.1in, label={}]}
\newcommand{\resumeListEndNum}{\end{enumerate}}
\newcommand{\resumeItemListStartNum}{\begin{enumerate}[label=(\arabic*)]}
\newcommand{\resumeItemListEndNum}{\end{enumerate}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Chun Chet Ng} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:60124202083}{+60124202083}
    $|$
    \faAt \hspace{.5pt} \href{mailto:ngchunchet95@gmail.com}{ngchunchet95@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/chunchet-ng/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/chunchet-ng}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://chunchet-ng.github.io}{Website}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Universiti+Malaya/@3.1217233,101.6536844,17z/data=!3m1!4b1!4m6!3m5!1s0x31cdb47024217187:0x1e85ebc65d47d641!8m2!3d3.1217233!4d101.6536844!16zL20vMDFxNDF6}{Kuala Lumpur, Malaysia}
\end{center}

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    % \resumeEducationHeading
    %   {University of Malaya
    %   \normalfont{(Admission rate: 0.09\%)}
    %   }{Kuala Lumpur, Malaysia}
    %   {B.Sc. in Electrical and Electronics Engineering;   \textbf{GPA: 3.73/4.00}}{Sept. 2018 \textbf{--} DEC 2023 (Expected)}
    %   {Minor Degree in Computer Engineering;   \textbf{GPA: 3.89/4.00}}{Oct 2020 \textbf{--} Jun 2023 (Expected)}
        % \resumeItemListStart
            % \resumeItem{\textbf{Relevant coursework:} Calculus I-II, Matrix Theory, Differential Equations, Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering}
        % \resumeItemListEnd
        
    \resumeSubheading
      {University of Malaya}{Kuala Lumpur, Malaysia}
      {Ph.D. in Artificial Intelligence (Computer Vision)}{Sept. 2018 \textbf{--} Dec. 2024}

    \resumeEducationHeading
      {Tunku Abdul Rahman University of Management \& Technology}{Kuala Lumpur, Malaysia}
      {Bachelor of Computer Science (Honours) in Software Engineering; \textbf{CGPA: 3.97/4.00}}{May. 2015 \textbf{--} May. 2017}
      {Diploma in Science (Computer Science and Mathematics); \textbf{CGPA: 3.97/4.00}}{May. 2013 \textbf{--} May. 2015}
    
  \resumeSubHeadingListEnd

%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {University of Malaya}{Kuala Lumpur, Malaysia}
      {Research Assistant}{Sept. 2018 \textbf{--} Dec. 2023}
        \resumeItemListStart
            \resumeItem{Under the supervision of \href{http://cs-chan.com/}{\color{blue}Prof. Chan Chee Seng} from the Centre of Image and Signal Processing Lab.}
            \resumeItem{Researched on the scene text detection, recognition and spotting methods. With also studies on low-light image enhancement-related works. Proposed a few notable scene text datasets, including the introduction of novel text datasets such as ArT, EST-VQA, and ICText.}
            \resumeItem{My Ph.D. thesis title is \enquote{Optical Character Recognition Under Challenging Lighting Conditions}.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Stealth Startup}{Kuala Lumpur, Malaysia}
      {Classified}{Apr. 2024 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Spearheaded the AI and Engineering team to deliver an OCR-based financial technology product.}
        \resumeItemListEnd

    \resumeSubheading
      {Etch Media}{Kuala Lumpur, Malaysia}
      {Vice President of Engineering}{Oct. 2023 \textbf{--} Mar. 2024}
        \resumeItemListStart
            \resumeItem{Worked on development and integration of backend services with AI services for car recognition (make, model, colour) and face recognition (gender, age, emotion).}
        \resumeItemListEnd

    \resumeSubheading
      {AkiraKan Limited}{Kuala Lumpur, Malaysia}
      {Part Time ML/AI Research Scientist (3D \& AI)}{Jan. 2023 \textbf{--} Sept. 2023}
        \resumeItemListStart
            \resumeItem{Handled OCR-related projects including lamp post ID extraction and license plate recognition based on traffic scene images.}
        \resumeItemListEnd
        
    \resumeSubheading
      {ViTrox Corporation Bhd.}{Penang, Malaysia}
      {Research Intern}{Mar. 2020 \textbf{--} Dec. 2022}
        \resumeItemListStart
            \resumeItem{Interned at the Centre of Excellence department and worked on industrial OCR problems. Specifically, the study of OCR methods in industrial use cases to detect and recognize defective characters accurately on chip images.}
            \resumeItem{Organized an international OCR competition, ICDAR 2021 RRC - ICText together with Baidu and a few partner universities. Leading to the creation of the largest Integrated Text on Chips Dataset (ICText).}
            \resumeItem{Proposed a novel curriculum-learning-based training strategy to improve character recognition methods' performance on the ICText dataset where most of the images contain texts with aesthetic defects such as low contrast, blurry and broken. Two publications are the output of this research project.}
            \resumeItem{Supervised a few undergraduate interns to work on image classification and object detection projects.}
        \resumeItemListEnd
    
    % \vspace{15pt}
    \resumeSubheading
      {Theta Service Partner Sdn. Bhd.}{Kuala Lumpur, Malaysia}
      {Intern Software Engineer}{Feb. 2017 \textbf{--} Aug. 2017}
        \resumeItemListStart
            \resumeItem{Joined the Centre of Excellence department to work on the bank loan software system. I was mainly responsible for bug fixing, implementing customers' requirements, and writing test cases. The tech stack involves Angular as the front-end framework with C\# and Java as the back-end.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------- VOLUNTEER EXPERIENCE -----------

\section{Volunteer Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Dharma Drum Mountain Buddhist Centre}{Kuala Lumpur, Malaysia}
      {Software Engineer}{2017 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Completed an internal E-receipt system to keep track of all received donations and payments.}
            \resumeItem{Created an e-commerce website to allow the selling of books online and the acceptance of online donations.}
            \resumeItem{Setup and migrated the legacy email systems to GSuite for NGO. These upgrades have greatly improved their workflow and services during the COVID-19 pandemic.}
            \resumeItem{Periodic update and maintenance of all IT software and systems.}
        \resumeItemListEnd
        
    \resumeSubheading
      {Dhamma Earth Malaysia}{Kuala Lumpur, Malaysia}
      {IT Volunteer}{2019 \textbf{--} 2020}
        \resumeItemListStart
            \resumeItem{Initial setup of the organization's main website.}
            \resumeItem{Developed a web application to keep track of allowable requisites (the accounts of Buddhist monks and nuns).}
        \resumeItemListEnd
        
  \resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Perfect Half Million Beauty Product Image Recognition Challenge 2018:}{ Ranked 4th out of 13 teams. Implemented Mask-RCNN and carry out feature extraction using various CNN models.} \\ \vspace{3pt}
        
        \textbf{HACK2HIRED Software Hackathon 2017:}{ Represented my team to present to panel judges and won second runner-up as a team. Implemented a production line monitoring system within 24 hours.} \\ \vspace{3pt}
        
        \textbf{Pecipta 2017:}{ Won a Bronze Medal with my Bachelor's Degree's Final Year Project, titled \enquote{Malaysia’s Car Plate Recognition System}. I am the leader of a team with 4 members where I implemented a license plate recognition algorithm using KNN and the proposed method outperforms the existing methods significantly.} \\ \vspace{3pt}
        
        \textbf{Hilti's FYP Competition 2016:}{ Won Second Runner Up with \enquote{Malaysia’s Car Plate Recognition System}.} \\ \vspace{3pt}
        
        \textbf{TARUMT's FYP Showcase 2016:}{ Won First Runner Up with \enquote{Malaysia’s Car Plate Recognition System}.} \\ \vspace{3pt}
        
        \textbf{Bachelor Degree \& Diploma:}{ President’s Award Winner as the best graduate for the year of 2017/2018. Book Prize Award Winner for diploma and degree (highest CGPA). President’s List for every semester during diploma and degree.} 
        
    }}
  \resumeSubHeadingListEnd

%----------- CONFERENCE -----------

% \section{Research Publications - Conference Papers}
%     \vspace{3pt}
%     \resumeSubHeadingListStart

%       \resumeProjectHeading
%         {\textbf{Filters and Fractals} $|$ \emph{\href{https://github.com/arasgungore/filters-and-fractals}{\color{blue}GitHub}}}{}
%           \resumeItemListStart
%             \resumeItem{A C project which implements a variety of image processing operations that manipulate the size, filter, brightness, contrast, saturation, and other properties of PPM images from scratch.}
%             \resumeItem{Added recursive fractal generation functions to model popular fractals including Mandelbrot set, Julia set, Koch curve, Barnsley fern, and Sierpinski triangle in PPM format.}
%           \resumeItemListEnd
      
%       \resumeProjectHeading
%         {\textbf{Chess Bot} $|$ \emph{\href{https://github.com/arasgungore/chess-bot}{\color{blue}GitHub}}}{}
%           \resumeItemListStart
%             \resumeItem{A C++ project in which you can play chess against an AI with a specified decision tree depth that uses alpha-beta pruning algorithm to predict the optimal move.}
%             \resumeItem{Aside from basic moves, this mini chess engine also implements chess rules such as castling, en passant, fifty-move rule, threefold repetition, and pawn promotion.}
%           \resumeItemListEnd
      
%       \resumeProjectHeading
%         {\textbf{Rocket Flight Simulator} $|$ \emph{\href{https://github.com/arasgungore/rocket-flight-simulator}{\color{blue}GitHub}}}{}
%           \resumeItemListStart
%             \resumeItem{A Simulink project which can accurately simulate the motion of a flying rocket in one-dimensional space.}
%             \resumeItem{The project implements the forces acting on a rocket which are drag, weight, and thrust as subsystems that take time-variant parameters into consideration such as distance from the center of Earth, mass and velocity of the rocket, and air density at different layers of Earth{\textquotesingle}s atmosphere.}
%           \resumeItemListEnd
      
%       \resumeProjectHeading
%         {\textbf{Netlist Solver} $|$ \emph{\href{https://github.com/arasgungore/netlist-solver}{\color{blue}GitHub}}}{}
%           \resumeItemListStart
%             \resumeItem{A MATLAB project that uses modified nodal analysis (MNA) algorithm to calculate the node voltages of any analog circuit without dependent sources given in netlist format.}
%             \resumeItem{Added a module that sweeps the resistance of a load resistor, plots power dissipation as a function of load resistance, and finds the resistance value corresponding to maximum power.}
%           \resumeItemListEnd
      
%       \resumeProjectHeading
%         {\textbf{Unprecedented Usage of Pre-trained CNNs on Beauty Product} $|$ \href{https://github.com/arasgungore/CMPE250-projects}{\color{blue}[paper]}}{}
%           \resumeItemListStart
%             \resumeItem{Five Java projects assigned for the Data Structures and Algorithms (CMPE 250) course in the Fall 2021-22 semester.}
%             \resumeItem{These projects apply DS\&A concepts such as discrete-event simulation (DES) using priority queues, Dijkstra's shortest path algorithm, Prim's algorithm to find the minimum spanning tree (MST), Dinic's algorithm for maximum flow problems, and weighted job scheduling with dynamic programming to real-world problems.}
%           \resumeItemListEnd
      
%     \resumeSubHeadingListEnd


\section{Research Publications - Conference Papers}
    \vspace{3pt}
    \resumeListStartNum
    \item{
        \resumeItemListStartNum
            \resumeItem{Hsu, Po-Hao$^*$, Che-Tsung Lin$^*$, \textbf{Chun Chet Ng$^*$}, Jie Long Kew, Mei Yih Tan, Shang-Hong Lai, Chee Seng Chan, and Christopher Zach. \enquote{Extremely low-light image enhancement with scene text restoration.} In 2022 26th International Conference on Pattern Recognition (ICPR), pp. 317-323. IEEE, 2022.}
            \resumeItem{\textbf{Chun Chet Ng}, Akmalul Khairi Bin Nazaruddin, Yeong Khang Lee, Xinyu Wang, Yuliang Liu, Chee Seng Chan, Lianwen Jin, Yipeng Sun, and Lixin Fan. \enquote{ICDAR 2021 Competition on Integrated Circuit Text Spotting and Aesthetic Assessment.} In Document Analysis and Recognition–ICDAR 2021: 16th International Conference, Lausanne, Switzerland, September 5–10, 2021, Proceedings, Part IV 16, pp. 663-677. Springer International Publishing, 2021.}
            \resumeItem{Wang, Xinyu, Yuliang Liu, Chunhua Shen, \textbf{Chun Chet Ng}, Canjie Luo, Lianwen Jin, Chee Seng Chan, Anton van den Hengel, and Liangwei Wang. \enquote{On the general value of evidence, and bilingual scene-text visual question answering.} In Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition, pp. 10126-10135. 2020.}
            \resumeItem{Chng, Chee Kheng, Yuliang Liu, Yipeng Sun, \textbf{Chun Chet Ng}, Canjie Luo, Zihan Ni, ChuanMing Fang et al. \enquote{Icdar2019 robust reading challenge on arbitrary-shaped text-rrc-art.} In 2019 International Conference on Document Analysis and Recognition (ICDAR), pp. 1571-1576. IEEE, 2019.}
            \resumeItem{Sun, Yipeng, Zihan Ni, Chee-Kheng Chng, Yuliang Liu, Canjie Luo, \textbf{Chun Chet Ng}, Junyu Han et al. \enquote{Icdar 2019 competition on large-scale street view text with partial labeling-rrc-lsvt.} In 2019 International Conference on Document Analysis and Recognition (ICDAR), pp. 1557-1562. IEEE, 2019.}
            \resumeItem{Lim, Jian Han, Nurul Japar, \textbf{Chun Chet Ng}, and Chee Seng Chan. \enquote{Unprecedented usage of pre-trained CNNs on beauty product.} In Proceedings of the 26th ACM international conference on Multimedia, pp. 2068-2072. 2018.}
      \resumeItemListEndNum}
      \vspace{0.2cm}
      \emph{    $^*$Indicates equal contribution.}
    \resumeListEndNum

  
\section{Research Publications - Journal Papers}
    \vspace{3pt}
    \resumeListStartNum
    \item{
        \resumeItemListStartNum
            \resumeItem{\textbf{Chun Chet Ng$^*$}, Che-Tsung Lin$^*$, Zhi Qin Tan, Wan Jun Nah, Xinyu Wang, Jie Long Kew, Pohao Hsu, Shang Hong Lai, Chee Seng Chan, and Christopher Zach. \enquote{Text In the Dark: Extremely Low-Light Text Image Enhancement.} In Signal Processing: Image Communication, vol. 130, pp. 117222, 2025.}
            \resumeItem{\textbf{Chun Chet Ng$^*$}, Che-Tsung Lin$^*$, Zhi Qin Tan, Xinyu Wang, Jie Long Kew, Chee Seng Chan, and Christopher Zach. \enquote{When IC Meets Text: Towards a Rich Annotated Integrated Circuit Text Dataset.} In Pattern Recognition, vol. 147, pp. 110124, 2024.}
      \resumeItemListEndNum}
      \vspace{0.2cm}
      \emph{    $^*$Indicates equal contribution.}
    \resumeListEndNum

%----------- Review Experiences -----------

\section{Review Experiences}
  \vspace{2pt}
  \resumeListStart
    \item{
        \resumeItemListStart
            \resumeItem{PR 2024.}
            \resumeItem{PR 2023.}
            \resumeItem{AAAI 2022, 2023.}
            \resumeItem{PR 2022.}
            \resumeItem{CVPR 2021, 2022.}
            \resumeItem{ECCV 2022.}
            \resumeItem{ICCV 2021.}
            \resumeItem{BMVC 2021.}
            \resumeItem{ICDAR 2019, 2021.}
      \resumeItemListEnd}
  \resumeListEnd

%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming: }{Python, C\#, Java, SQL} \\ \vspace{3pt}
        
        \textbf{Technologies: }{PyTorch, NumPy, Matplotlib, Pandas, TensorFlow, Django} \\ \vspace{3pt}
        
        \textbf{Languages: }{Mandarin (Native), English (Professional), Malay (Fluent)}
        
        % \textbf{Frameworks}{: X, X, X} \\
        % \textbf{Developer Tools}{: X, X, X} \\
        % \textbf{Libraries}{: X, X, X} \\
        % \textbf{Applications}{: X, X, X}
    }}
  \resumeSubHeadingListEnd

%----------- Supplementary AI Certificates -----------

\section{Supplementary AI Certificates}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{MOOC:}{ Coursera Andrew Ng’s Machine Learning, Deep Learning
Specialization, DeepLearning.AI Tensorflow Developer} \\ \vspace{3pt}
        
        \textbf{Summer Schools:}{ Southeast Asia Machine Learning School 2019, Oxford Machine Learning Summer School 2022}
    }}
  \resumeSubHeadingListEnd

%----------- CERTIFICATES -----------

% \section{Certificates}
%   \resumeSubHeadingListStart
%     \resumeOrganizationHeading
%       {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}    
%   \resumeSubHeadingListEnd

%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
  % \resumeSubHeadingListEnd
  
%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd
  
%----------- REFERENCES -----------

% \section{References}
  % \resumeSubHeadingListStart
  % \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}